\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-05-15 standardmodel.tex
TODO: 1. finish inh-rules type setting 2. examples for verification 3. formalize argument for canonicity

@@

We omit the model here for extensible inductive type and inheritance judgement because they require inductive facility in meta-logic. In set theory, that would be using \textit{rule sets}~\citep{timany2017consistency,aczel1998relating}, which would be more confusing for the reader. In appendix we will use the native inductive notion from Agda to construct models.

>>>>

Note that, since every piece is intrinsic, $\denotesS{t}$ means the same as $\denotesS{\goodTerm{\Gamma}{t}{T}}$.

@@

We omit the model here for extensible inductive type and inheritance judgement because they require inductive facility in meta-logic. In set theory, that would be using \textit{Rule sets}~\citep{timany2017consistency,aczel1998relating}, which would be more confusing for the reader. In appendix we will use the native inductive notion from Agda to construct models.
